---
title: "Reproducible Document"
author: "DanielAJ"
format: html
---

```{r setup}
#| message: false
#| warning: false
library(tidyverse)
post_meal_data <- read_csv2(here::here("data/post-meal-insulin.csv"))
```


##Writing R code



```{r}
2 + 2
```

##About me

-   Daniel Alexander Jørgensen
-   Esbjerg & Grindsted Sygehus

**I want to learn R**

*I am learning R*

##Simple Code
```{r}
3 * 3
```
##Testing for Git

its cold outside


##Showing the data

```{r}
post_meal_data

glimpse(post_meal_data)
```


## Plot one continous variabel

```{r}
#| fig-cap: "Distribution of BMI"
#| label: fig-bmi-histo
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
```

See @fig-bmi-histo

## Exercise: discrete plots
```{r}
#| fig-cap: "Glykemi"
#| label: fig-Glykemi
ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```

See @fig-Glykemi above for a cool plot!

## Plotting two discrete variables 

```{r}
ggplot(post_meal_data, aes(x = Group, fill = as.character(glykemi))) +
  geom_bar(position = position_dodge())
```

## Side by side plots

```{r fig-BMI-glycemia}
#| fig-cap: "BMI and Glycemia, side by side"
#| fig-subcap:
#|  - "Distribution of BMI."
#|  - "Number of those with Glycemia"
#| layout-ncol: 2
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```
## PLotting two continuous variables 

```{r}
#| fig-cap: "Scatter plot of BMI and the area under the curve for glucose"
#| label: fig-bmi-auc-pg
ggplot(post_meal_data, aes(x = BMI, y = auc_pg)) +
  geom_point() +
  geom_smooth()
```
