---
title: "Reproducible Document"
author: "DanielAJ"
format: html
---

```{r setup-chunk}
#| message: false
#| warning: false
library(tidyverse)
post_meal_data <- read_csv2(here::here("data/post-meal-insulin.csv"))

small_post_meal_data <- select(post_meal_data, id, Age, BMI, Group, auc_pg, auc_ins, glykemi)

tidier_post_meal_data <- small_post_meal_data %>%
  rename(
    auc_glucose = auc_pg,
    auc_insulin = auc_ins
  ) %>%
  filter(glykemi == 0) %>%
  select(-glykemi)

tidied_post_meal_data <- tidier_post_meal_data %>%
  mutate(
    insulin_glucose_ratio = auc_insulin / auc_glucose,
    group = if_else(Group == "CTR", "Control", "First-degree relative")
  )
```


##Writing R code



```{r}
2 + 2
```

##About me

-   Daniel Alexander Jørgensen
-   Esbjerg & Grindsted Sygehus

**I want to learn R**

*I am learning R*

##Simple Code
```{r}
3 * 3
```
##Testing for Git

its cold outside


##Showing the data

```{r}
post_meal_data

glimpse(post_meal_data)
```


## Plot one continous variabel

```{r}
#| fig-cap: "Distribution of BMI"
#| label: fig-bmi-histo
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
```

See @fig-bmi-histo

## Exercise: discrete plots
```{r}
#| fig-cap: "Glykemi"
#| label: fig-Glykemi
ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```

See @fig-Glykemi above for a cool plot!

## Plotting two discrete variables 

```{r}
ggplot(post_meal_data, aes(x = Group, fill = as.character(glykemi))) +
  geom_bar(position = position_dodge())
```

## Side by side plots

```{r fig-BMI-glycemia}
#| fig-cap: "BMI and Glycemia, side by side"
#| fig-subcap:
#|  - "Distribution of BMI."
#|  - "Number of those with Glycemia"
#| layout-ncol: 2
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```
## PLotting two continuous variables 

```{r}
#| fig-cap: "Scatter plot of BMI and the area under the curve for glucose"
#| label: fig-bmi-auc-pg
ggplot(post_meal_data, aes(x = BMI, y = auc_pg)) +
  geom_point() +
  geom_smooth()
```

## Selecting data

```{r}
select(post_meal_data, Age)

select(post_meal_data, Age, BMI, Weight)

select(post_meal_data, -Group)

select(post_meal_data, starts_with("PG"))
select(post_meal_data, ends_with("DXA"))
select(post_meal_data, contains("0"))
```


## Filtering data 

```{r}
small_post_meal_data %>%
  filter(glykemi == 1)

small_post_meal_data %>%
  filter(BMI >= 25)

small_post_meal_data %>%
  filter(Group == "CTR")

small_post_meal_data %>%
  filter(Group == "CTR" | BMI >= 25)
```


## Renaming Columns

```{r}
small_post_meal_data %>%
  rename(
    auc_glucose = auc_pg,
    auc_insulin = auc_ins
  )
```

```{r}
# Task 1.
post_meal_data |>
  select(contains("0GGT"))

# Task 2.
post_meal_data |>
  select(contains(".."), -contains("..."))

# Task 3.
post_meal_data |>
  rename(
    P.Glucose.minus5.OGTT = P.Glucose..5.OGTT,
    Insulin.minus5.OGTT.X = Insulin..5.OGTT.X
  )

# Task 4.
post_meal_data |>
  select(id, BMI, Length, Weight, Age)
```


## Modifying data

```{r}
tidier_post_meal_data %>%
  mutate(insulin_glucose_ratio = auc_insulin / auc_glucose)

tidier_post_meal_data %>%
  mutate(
    insulin_glucose_ratio = auc_insulin / auc_glucose,
    group = if_else(Group == "CTR", "Control", "First-degree relative")
  )
```


## Practice with filter and mutate

```{r}
# Task 1.
post_meal_data |>
  filter(BMI >= 25 & BMI <= 40 & Group == "FDR")

# Task 2.
post_meal_data |>
  mutate(
    percentage_body_fat = (Fat.mass.DXA / Weight) * 100
  ) |>
  filter(percentage_body_fat > 30)
```

## Visualizing with a jitter plot

```{r}
tidied_post_meal_data %>%
  mutate(overweight = if_else(BMI >= 25, "Overweight", "Not overweight")) %>%
  ggplot(aes(x = overweight, y = insulin_glucose_ratio)) +
  geom_jitter()
```

## Plotting three or more variables

```{r}
tidied_post_meal_data %>%
  filter(BMI < 30) %>%
  mutate(young = if_else(Age < 40, "Young", "Old")) %>%
  ggplot(aes(x = BMI, y = insulin_glucose_ratio, color = Group)) +
  geom_point() +
  facet_grid(rows = vars(young)) +
  labs(
    x = "Body mass index (BMI)",
    y = "Insulin to glucose ratio"
  )
```


## Make Multi-dimmensional plot

```{r}
#| label: fig-multidimensional
#| fig-cap: "Two, mult-dimensional plots of our data."
#| fig-subcap:
#|   - "Distribution of percent body fat by group and age category."
#|   - "Relationship between BMI and bone mineral density, split by insulin sensitivity."
#| layout-ncol: 2
# Task 1.
post_meal_data |>
  mutate(
    percent_body_fat = (Fat.mass.DXA / Weight) * 100,
    young = if_else(Age < 40, "Young", "Old")
  ) |>
  ggplot(aes(x = Group, y = percent_body_fat, colour = young)) +
  geom_jitter(width = 0.2)

# Task 2.
post_meal_data |>
  mutate(
    insulin_glucose_ratio = (auc_ins / auc_pg),
    insulin_insensitive = if_else(insulin_glucose_ratio > mean(insulin_glucose_ratio), "insensitive", "sensitive")
  ) |>
  ggplot(aes(x = BMI, y = Bone.mineral.DXA, color = insulin_insensitive)) +
  geom_point() +
  geom_smooth() +
  facet_grid(cols = vars(insulin_insensitive))
```


## Color tasks in plots

## Changing plot color

```{r}
# Tasks 1. and 2.
post_meal_data |>
  mutate(hyperglycemia = if_else(glykemi == 1, "Yes", "No")) |>
  ggplot(aes(x = Group, fill = hyperglycemia)) +
  geom_bar(position = position_dodge()) +
  scale_fill_viridis_d("magma")

# Tasks 3. and 4.
post_meal_data |>
  ggplot(aes(x = auc_pg, y = auc_ins, colour = BMI)) +
  geom_point() +
  scale_colour_viridis_c("inferno")
```



## Calculating summary statistics 

```{r}
tidied_post_meal_data %>% 
  summarise(max_bmi = max(BMI),
            min_bmi = min(BMI))
```
## Summarize with group b

```{r}
tidied_post_meal_data %>% 
   group_by(Group) %>% 
  summarize(mean_age = mean(Age),
            mean_BMI = mean(BMI)) %>% 
  ungroup()

   
```

